Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-13 longoutput.tex
Use projection lemma

According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks.

@@

Now we combine the three Hamiltonians defined. First consider their kernels.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
Notice that (TODO need proof or no?)
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
We now define
$$K=(\spn\set{\psi_{circuit}})^\bot$$
and consider $H_{clock}\big|_K,H_{in}\big|_K,H_{prop}\big|_K$. That is, we restrict the following computations to the subspace $K$. We apply the projection lemma.
$$\exists J_{clock},
\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K)\geq
\lambda(H_{in}\big|_{K\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop},
\lambda(H_{in}\big|_K+J_{clock}H_{clock}\big|_K+J_{prop}H_{prop}\big|_K)\geq
\lambda(H_{in}\big|_{K\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_K)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$. It has the following properties.
\begin{itemize}
	\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$
\end{itemize}

>>>>

According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the second eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.

@@

Now we combine the three Hamiltonians defined. First consider their kernels.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
Notice that (TODO need proof or no?)
$$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\psi_{circuit}}$$
We now define
$$S=(\spn\set{\psi_{circuit}})^\bot$$
and consider $H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$. That is, we restrict the following computations to the subspace $S$. We apply the projection lemma.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(1)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$. It has the following properties.
\begin{itemize}
	\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
	\item $\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$ for $\ket\phi$ such that $\braket{\phi|\psi_{circuit}}=0$
	\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$
	\item $\norm{H_{circuit}}_{\max}=O(T^3)$
\end{itemize}
